Advice on describing Bayesian analysis of neutron and X-ray reflectometry

### 2022-11-11 src/tex/ms.tex
Correct formattiing
Remove unnecessary unskip

Either the full posterior chain or the thinned chain should be shared along with details of any autocorrelation analysis to accompany any Bayesian or sampling analysis. 
This will allow the best replication and verification of any results obtained from the data. 
Furthermore, large output files such as these chains can be easily shared using some versioned data repository, such as Zenodo \cite{european_zenodo_2013} or those available at specific institutions. 
Additionally, to allow the reader to quickly interpret the sampled posterior, a graphical description (such as that in Figure~\ref{fig:post}) should be included, at a minimum, in the supplementary information of the work. 
The importance of presenting the full posterior graphically lies in the ability to easily interpret correlations between parameters through this medium.
For example, in Figure 3, the ellipsoidal probability distribution (for the d/rho) parameters indicates correlation.
%
\begin{figure}
  \script{post.py}
  \includegraphics[width=\columnwidth]{figures/post.pdf}
  \caption{
    An example of a graphical depiction of the unthinned posterior as a corner plot (produced using the \texttt{corner.py} package \cite{foremanmackey_corner_2016}), representing a three-dimensional probability distribution showing the posterior distribution for the parameters of nickel magnetic scattering length density, nickel mass density, and nickel layer thickness, from the analysis of a nickel layer on a silicon block.
  }
  \label{fig:post}
\end{figure}
%

To report values for parameters and some form of statistical uncertainty, two approaches can be taken from the posterior chain. 
The first is to use some known statistical distribution that describes the samples well.
This is best defined for a normal distribution, for which there are statistical tests to check normality, such as the D'Agostino and Pearson's test \cite{dagostino_omnibus_1971,dagostino_tests_1973} (which is available in the SciPy library as \texttt{scipy.stats.normaltest} \cite{virtanen_scipy_2020}).
As with all statistical tests, this requires some threshold value to be defined to reject the null hypothesis, for this value we recommend \num{0.001} but accept that this is at the discretion of the user. 
If the parameter distribution passes a statistical test for a given distribution type, this can be quoted in the work, with information about the distribution type and the threshold value used, and the distribution can be described based on fitted parameters of the distribution as is discussed above for the Gaussian distribution. 
For example, the three parameters in Figure~\ref{fig:post} pass this statistical tests, with $p$-values of greater than \num{0.01} when \num{1000} random samples are used, therefore we can quote the parameters as normal distributions; \variable{output/mag_sld.txt}\unskip, \variable{output/density.txt}\unskip, and \variable{output/thick.txt}\unskip.

>>>>

Either the full posterior chain or the thinned chain should be shared along with details of any autocorrelation analysis to accompany any Bayesian or sampling analysis. 
This will allow the best replication and verification of any results obtained from the data. 
Furthermore, large output files such as these chains can be easily shared using some versioned data repository, such as Zenodo \cite{european_zenodo_2013} or those available at specific institutions. 
Additionally, to allow the reader to quickly interpret the sampled posterior, a graphical description (such as that in Figure~\ref{fig:post}) should be included, at a minimum, in the supplementary information of the work. 
The importance of presenting the full posterior graphically lies in the ability to easily interpret correlations between parameters through this medium.
For example, in Figure 3, the ellipsoidal probability distribution (for the $d$/$\rho$) parameters indicates correlation.
%
\begin{figure}
  \script{post.py}
  \includegraphics[width=\columnwidth]{figures/post.pdf}
  \caption{
    An example of a graphical depiction of the unthinned posterior as a corner plot (produced using the \texttt{corner.py} package \cite{foremanmackey_corner_2016}), representing a three-dimensional probability distribution showing the posterior distribution for the parameters of nickel magnetic scattering length density, nickel mass density, and nickel layer thickness, from the analysis of a nickel layer on a silicon block.
  }
  \label{fig:post}
\end{figure}
%

To report values for parameters and some form of statistical uncertainty, two approaches can be taken from the posterior chain. 
The first is to use some known statistical distribution that describes the samples well.
This is best defined for a normal distribution, for which there are statistical tests to check normality, such as the D'Agostino and Pearson's test \cite{dagostino_omnibus_1971,dagostino_tests_1973} (which is available in the SciPy library as \texttt{scipy.stats.normaltest} \cite{virtanen_scipy_2020}).
As with all statistical tests, this requires some threshold value to be defined to reject the null hypothesis, for this value we recommend \num{0.001} but accept that this is at the discretion of the user. 
If the parameter distribution passes a statistical test for a given distribution type, this can be quoted in the work, with information about the distribution type and the threshold value used, and the distribution can be described based on fitted parameters of the distribution as is discussed above for the Gaussian distribution. 
For example, the three parameters in Figure~\ref{fig:post} pass this statistical tests, with $p$-values of greater than \num{0.01} when \num{1000} random samples are used, therefore we can quote the parameters as normal distributions; \variable{output/mag_sld.txt}, \variable{output/density.txt}, and \variable{output/thick.txt}.
